Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
Cleaner figures
Iter on figure
Iter on paper, and shorten biblio

\paragraph{Project vision}
%
Bridging the gap between machine learning research and applications

\cite{pedregosa2011}

Striving for ease-of-use and quality

Importance of API design \cite{buitinck2013ecml}

\paragraph{The python data ecosystem}
%
In a data analysis pipeline, machine learning is only a tiny bit of the
pipeline, although it is critical.

Great scientific and numeric ecosystem
\cite{oliphant2007python,varoquaux2013scipy}, but also text processing,
webservers

NumPy arrays \cite{vanderwalt2011}, SciPy, matplotlib. Cython
\cite{behnel2011cython}

@@

>>>>

\paragraph{Project vision}
%
Scikit-learn was born from the observation that most standard
machine-learning algorithms were out of reach of the users that could
most benefit from them: researchers --biologists, climate
scientists, experimental physicists-- or developers --for web
services or domain-specific applications.
%
Implementations mostly consisted of scattered piece of code to download
on researchers' web pages, with the notable exception
statistic-specific environments such as the R language \cite{Rmanual}, or
the Weka java library \cite{hall2009weka}.

Scikit-learn aims to bridge the gap between machine-learning research and
applications by providing a library, and not an environment, in a
general-purpose language, relying on domain-agnostic data structures
\cite{pedregosa2011}. Emphasis is put on quality and ease of use, which
implies focus on installation issues, documentation, and API design
\cite{buitinck2013ecml}. For the project to be usable in real-world
settings, computational performance is also a priority.

\paragraph{The Python data ecosystem}
%
Machine learning is only a small part of a data-analysis pipeline, and
scikit-learn nicely dovetails into the rich Python ecosystem: scientific
and numeric tools \cite{oliphant2007python,varoquaux2013scipy}, but also
text processing tools, web servers...
%
For its numerical needs, scikit-learn leverages NumPy arrays
\cite{vanderwalt2011} --data structures for efficient numerical
computation--, SciPy --a collection of classic numerical algorithms--,
matplotlib \cite{hunter2007matplotlib} --for scientific plotting-- and
Cython, to generate and call compiled code in a Python-like syntax
\cite{behnel2011cython}.

@@

\begin{figure}
    %\hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data}%

    \caption{Wage as a function of years of experience and education,
    data from \cite{berndt1991}}
\end{figure}

\begin{figure}
    %\hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data_random_forest}%

    \caption{Wage prediction from years of experience and education,
    using random forests}
\end{figure}

\begin{figure}
    \hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data_linear_svm}%

    \caption{Wage prediction from years of experience and education,
    using a linear SVM}
\end{figure}
